# Week 6 Short Answer Questions

## Esteban Lemus Wirtz 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

###Problem 12.1

```{r}
BabyNames %>% 
  group_by(sex,name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total))<=5)
```

###Problem 12.2
```{r}
PopularCounts <-
  BabyNames %>%
  group_by(year,name) %>%
  summarise(count=sum(count)) %>%
  mutate(frac_in_top_100= rank(desc(count)) <=100) %>%
  group_by(year, frac_in_top_100) %>%
  summarise(total= sum(count))
GlyphReady <-
  PopularCounts %>%
  spread( frac_in_top_100, total) %>%
  mutate(frac_in_top_100= `TRUE`/(`TRUE`+`FALSE`))
ggplot(data= GlyphReady, aes(x= year, y=frac_in_top_100))+geom_line()
```

###Problem 12.3
a) Summary 
b) Neither
c) Summary
d) Transformation
e) Transformation
f) Summary
g) Transformation
h) Summary 

###Problem 13.1
1) 8 vertices: Japan, China, USSR, Germany, France, UK, USA, Italy
2) There are 9 edges

###Problem 13.2
1) Vertices= A,B,C,D
2) Table 2 
3) Table 1: B and C are not directly connected.
Table 3: C needs to be twice oce for A to C and once for C to D. 

###Problem 13.3
The correct table is Table 2 because Table 3 has the wrong directions and Table 1 connects vertices that are not even connected.

###Problem 13.4
1. Exports
2. Population

###Problem 14.1

```{r}
ggplot(data=CPS85, aes(x=sex, y=wage))+geom_boxplot(aes(fill=sex))
```

###Problem 14.3
For women the height would be between 1.5 and 1.7 .
For men the height would be between 1.7 and 1.9. 

###Problem 14.7
```{r}
ggplot(data=CPS85, aes(y=wage, x=educ))+geom_point(aes(color=sex))+ stat_smooth(method="lm",aes(color=sex))+ylim(0,15)
```

###Problem 14.10
```{r}
ggplot(data=Galton, aes(x=height, group=sex))+geom_density(aes(color=sex, fill=sex),alpha=0.5)
```





