# Week 3 Project

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

```{r}

ggplot(data = CPS85, aes(x = exper, y=wage, color = married)) + geom_point() + facet_wrap( ~ sector) + xlim(0,20)

```

```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex, fill=sex),alpha=0.2) + facet_wrap(~ pregnant)
```

## Wrangling 
Question 1
```{r}
diamonds %>%
  group_by(color) %>%
  summarise(avg_carat=mean(carat)) %>%
  arrange(desc(avg_carat)) %>%
  head(1)
  
```
The largest color of diamonds in terms of carat seems to be color "J"
Question 2
```{r}
diamonds %>%
  group_by(clarity) %>%
  summarise(avg_table=mean(table)) %>%
  arrange(desc(avg_table)) %>%
  head(1)
```
The clarity of diamonds has the largest average “table” per carat is I1. 
## Voting 

Question 1
```{r}
nrow(Minneapolis2013)
```
There are 80101 cases in this data set. 

Question 2
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(votes=n())%>%
  arrange(desc(votes)) %>%
    head(5)
```
The top 5 candidates are shown in the graph above.

Question 3
The number of ballots marked as undervote are as follows:\

For first choice:
```{r}
Minneapolis2013 %>%
  filter(First=="undervote") %>%
  group_by(First)%>%
  summarise(under_first=n())
```

For second choice:
```{r}
Minneapolis2013 %>%
  filter(Second=="undervote") %>%
  group_by(Second)%>%
  summarise(under_second=n())
```

For third choice:
```{r}
Minneapolis2013 %>%
  filter(Third=="undervote") %>%
  group_by(Third)%>%
  summarise(under_third=n())
```

Question 4
The top 3 Second vote selections among people who voted for Betsy Hodges as their first choice are as follows.
```{r}
Minneapolis2013 %>%
  filter(First=="BETSY HODGES") %>%
  group_by(Second) %>%
  summarise(votes=n())%>%
  arrange(desc(votes))%>%
  head(3)
```

Question 5
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(avg=base::mean(First=="undervote")) %>%
  arrange(desc(avg))%>%
  head(1)
```
The precinct with the highest fraction of first vote sections is precinct P-6C.
