# Week 7 Short Answer Questions

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(mosaicData)
```
##Problem 15.1
a)
```{r}
lubridate::mdy("April 30,1777")- lubridate::mdy("January 2,1996")
```
b)
```{r}
lubridate::mdy("06-23-1912")- lubridate::mdy("January 2,1996")
```
c)
```{r}
lubridate::dmy("3 March, 1847")- lubridate::mdy("January 2,1996")
```
d)
```{r}
lubridate::mdy_hm("November 11, 1918 at 11:00 am")- lubridate::mdy_hm("January 2,1996 at 11:00 am")
```
e)
```{r}
lubridate::mdy("July 20, 1969")- lubridate::mdy("January 2,1996")
```

##Problem 15.2  
All of the values given in the example have some sort of punctuation or characters. Thus we can only use tidyr::extract_numeric.
a)
```{r}
tidyr::extract_numeric("42,659.30")
```
b)
```{r}
tidyr::extract_numeric("17%")
```
c) 
```{r}
as.numeric("19")
```

d)
```{r}
tidyr::extract_numeric("$100")
```

e)
```{r}
tidyr::extract_numeric("9.8 m/seconds square")
```
f)
```{r}
tidyr::extract_numeric("9.8 m/s^2")
```
g) ASK ASK

tidyr::extract_numeric("6.62606957*10^-34 m2 kg/s")

h)
```{r}
as.numeric("6.62606957e-34")
```
i)
```{r}
tidyr::extract_numeric("42.659,30")
```

##Problem 16.1
1) Boys' names ending with a vowel:
```{r}
BoysVowel <-
  BabyNames %>%
  filter(sex=="M") %>%
  group_by(name) %>%
  filter(grepl("[aeiou]$", name))%>%
  summarise(total=sum(count))%>%
  arrange(desc(total))%>%
  head(10)
```

2) Names ending with "joe" or "jo"
```{r}
joeNames <-
  BabyNames %>%
  group_by(name) %>%
  filter(grepl(".*(jo$|joe$)",name)) %>%
  summarise(total=sum(count))%>%
  arrange(desc(total))%>%
  head(10)
```

##Problem 16.2
This pattern would produce a string of numbers that starts with any digit except for 1 and 0 and is follow by 2 more digits. Then there is a ".","-" or "space" followed by three digits and again a ".","-" or "space" followed by four digits. This would match the different ways people write telephone numbers. The componenents of strings being extracted are punctuation and numbers.

##Problem 16.3
1. Each string will have two letters because the pattern is a letter plus another one from the list.
2. Thre wil be 61 patterns which is the number of all the letters within the lists.
3. These are all the state abbreviations in the USA.



