# Week 4 Short Answer Questions

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Chapter 8
8.1
a) Add a layer of glyphs
b) Add a layer of glyphs
c) Construct the graphics frame
d) Change the scale for the frame
e) Set an axis label
f) Divede the frame into facets
g) Add a layer of glyphs
h) Construct the graphics frame

8.2
```{r}
library(mosaicData)
library(ggplot2)
```
Graph 1
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point(aes(shape=married))+
  facet_wrap(~sector)+ylim(0,30)
```
Graph 2
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point()+
  facet_grid(sex~married)+ylim(0,40)

```
8.3 
Graph A
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point()+ylim(0,30)
```
Graph B
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point(aes(shape=sex))+ylim(0,30)
```
Graph C  ASK AYOUB
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point(aes(shape=sex))+
  facet_grid(married~.)+ylim(0,30)
```
Graph D
```{r}
CPS85 %>%
  ggplot(aes(y=wage, x=age))+
  geom_point(aes(shape=married))+ylim(0,30)
```


##Chapter 9
9.1 
a) Summary Function
b) Data Verb
c) Quick Presentation ASK LE LION
d) Transformation ASK WHAT MEAN WOULD BE 
e) Data Verb
f) Quick Presentatoin
g) Summary Function
h) Transformation
i) Quick Presentation ASK LE LION 

9.3
1. To find the color of diamonds that is the largest on average
```{r}
diamonds %>%
  group_by(color)%>%
  summarise(avg=mean(carat))%>%
  head(1)
```
1. To find the clarity of diamonds that has the largest average table per carat  ASK ASK 
```{r}
diamonds %>%
  group_by(color)%>%
  summarise(avg=mean(table))%>%
  head(1)
```

