# Week 3 Short Answer Questions

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

##Chapter 5 
5.1 
```{r}
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9) +facet_grid(~race)
```
5.2 
```{r}
WorldMap(data=HappinessIndex, key="country", fill="corruption")
```

###Chapter 6
6.5
b.State and Polling Organization 

6.6
d. Glyph: Rectangle. Graphical attribute: color and text.

6.7 
e.Date of the poll 

6.8
```{r}
Small <-
  NCHS %>%
  sample_n(size=5000)
ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker) 
```

###Chapter 7

7.1
a) data %>% summarise(avg=mean(variable))
b) mutate() 
c) arrange(desc(variable)) 
d) filter()
e) select()
f) group_by()%>% summarise()

7.4 
a) BabyNamees is the wrong dataset and group_by has a string inside and it should be the name of a variable in the dataset.
b) Tmp is repeated in the summarise part. Tmp should only appear once in the line where it is assigned to a value.
c) The %>% is missing.

7.5
a) BabyNames%>%
   arrange(sex,count)
b) BabyNames%>%
   filter(sex=="F") 
c)  BabyNames%>%
   filter(sex=="M", count>n) 
   *n could be greater than 22.
d)  BabyNames%>%
  summarise(total= sum(count)
e) BabyNames%>%
   select(name,count)

7.7
a) BabyNames%>%
   group_by(year, sex)%>%
   summarise(total=sum(count))
No need to write the dataset again, R already knows we are working on it.
b) ZipGeography%>%  # The mistake was here they had a <- instead of the pipe.
   group_by(State)%>%
   summarise(pop=sum(Population))
c) Minneapolis2013 %>%
      group_by(First) %>%  # The mistake was here they had a <- instead of the pipe.
      summarise(voteReceived=n())
d) The order is incorrect
Minneapolis2013 %>%
      group_by(First) %>%  
      summarise(voteReceived=n())
7.11
a) sex, count, mean_age
b) diagnosis, count, mean_age
c) sex,diagnosis, count, mean_age
d) age,diagnosis, count, mean_age
c) age, count, mean_age

7.12
1. nrow()
2. names(dataset)
3. help(dataset)
4.library(package)
5. group_by
6 group_by(variable)%>% summarise(coun= sum(variable))
