# Week 5 Short Answer Questions

##Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

### Problem 10.1 
Since we are joining two tables together we need to include two tables in our code.

### Problem 10.2
The tables have a different number of cases, so they cannot be linked to each other side by side. 

### Problem 10.3 
1. Table B, since on a row we have country and the value for both years next to each other, so it is visually easy to compare the values, since they are next to each other.
2. Table C, since we would join each country to ContinentData and then we would just sum one single column. 

### Problem 11.1   
a) Table 1: Male/Female babies named "Name" in a year
Table 2: Babies named "Name"in a year and their gender
Table 3: Babies named "Name" with a specific sex born in a 1912 and 2012 
b) Narrow= Version One,  Wide= Version 2
c) Sex
d) Because Version One is the Narrow Version so there is no need to have F and M variables or year varibles (different years) per case.
e) Because they have different variables per case.
f) Year
g) Sex and number of babies
nbabies
From each case and year

### Problem 11.3 
a) Narrow:C Wide:A (Country is expanded)
b) Narrow:C Wide:B (Year is expanded)
c) They are the same relative to each other.

### Problem 11.4  
When       sbp
subject    BHO
subject    GWB
subject    WJC
before     120
before     115
before     135
after      160
after      135
after      145

### Problem 11.5

```{r}
TablesData= load(url("http://tiny.cc/dcf/MeasTreatTables.rda"))
```

```{r}
OutputTable <-
  Measurements %>%
  left_join(Treatments) %>%
  mutate(when = ifelse(treatment_date<date, "after","before")) %>%
  spread(key=what,value=value)
```






