# Week 5 Project

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library(ggplot2)
```
<!-- put your content after this line -->

###Question 1
1) Toyota is a higher income source, since it pays more dividends
2) Yes, Toyota is the company who had a the highest appreciation and highest dividends, while Honda had the biggest depreciation and lowest dividends.

###Question 2: Getting Price Data
```{r}
companies <- c("XOM", "RDS-A", "CVX")
Prices <- 
  read_stock_prices(companies, what="daily",
                  start_year=2000, end_year=2015)
```

```{r}
ggplot(data=Prices,aes(y=close, x=date))+geom_line(aes(color=company))
```

###Question 3: Buy/Sell Profit
```{r}
a <- c("buy", "sell")
b <- ymd(c("2006-01-03","2014-12-30"))
Actions <- data.frame(action=a, date=b)
```


```{r}
Pricesx <- 
  Actions %>%
  left_join(Prices) %>%
  select(action, company, adj_close)%>%
  spread(key = action, value = adj_close)
```

```{r}
ProfitPercent <- 
  Actions %>%
  left_join(Prices) %>%
  select(action, company, adj_close)%>%
  spread(key = action, value = adj_close) %>%
  mutate(ProfitPercentage= ((sell/buy)*100))
```
###Question 4: Indexing Prices
```{r}
ref_date <- ymd("2005-01-03")
Reference <-
  Prices %>% 
  filter(date==ref_date) %>%
  select(company, standard=close)
```

Join Prices and Reference
```{r}
PricesRef <-
  Prices %>%
  left_join(Reference) %>%
  mutate(Index = close/standard)
```

```{r}
ggplot(data=PricesRef, aes(y=Index, x=date, color=company))+geom_line()
```


###Question 5: Dividends 
```{r}
Dividends <- 
  read_stock_prices(companies, what="dividends") 
```

Join Dividends to Actions using company to match:
```{r}
DividendsDates <-
  Dividends %>%
  left_join(Pricesx) %>%
  mutate(dividensPerStock= buy*dividends)
```

```{r}
DividendsDates%>%
  filter(date>ymd("2005-01-03")) %>%
  filter(date<ymd("2014-12-30")) %>%
  group_by(company) %>%
  summarise(totalDividends=sum(dividends))
```



