# Week 2 Project

## Esteban Lemus Wirtz

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r}
download.file("http://tiny.cc/dcf/Library-small.rda", 
              dest="Library-small.rda")
```
The data used in this mini-project was obtained from http://tiny.cc/dcf/Library-small.rda and 
contains records on books from the Macalester College library. 

##Basics
```{r}
load("Library-small.rda")

```

In the following chunk we will further exlpore the dataset used. We will obtain the number of rows from `Inv` and `Bks` and the names of the variables. This data is a subset of a bigger data set that includes data on how many times books have been borrowed. We also include a short summary of the datasets that tells us the number of cases and the names of the variables of the data.
```{r}
nrow(Inv)
nrow(Bks)
names(Inv)
names(Bks)

```

```{r}
Inv %>%
  group_by(Current.Status) %>%
  tally()
```
The above table tells us how many books have been withdrawn, the ones available, the missing ones and the ones on loan.

```{r}
Inv %>%
  group_by(Issued.Count) %>%
  tally()
```
This table tells us how many books have been borrowed 0, 1,2 ... times.  Issued count tells the number of times a book was borrowed and n is the number of books that have been borrowed that number of times.
